---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autogam

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/autogam)](https://CRAN.R-project.org/package=autogam)
[![R-CMD-check](https://github.com/tripartio/autogam/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tripartio/autogam/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

AutoGAM is a wrapper package for `mgcv` that makes it easier to create high-performing Generalized Additive Models (GAMs). With its central function `autogam()`, by entering just a dataset and the name of the outcome column as inputs, AutoGAM tries to automate as much as possible the procedure of configuring a highly accurate GAM at reasonably high speed, even for large datasets.

## Installation

You can install the development version of autogam like so:

``` r
# install.packages("devtools")
devtools::install_github("tripartio/autogam")
```

## Example

Here's a simple example using the `mtcars` dataset to predict `mpg`:

```{r example}
library(autogam)

ag <- autogam(mtcars, 'mpg')

summary(ag)
```


